\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-05-29 Report/notes.tex
changing report script and python, add plot to the report and lauched a massive computation
change report and and time on logs

>>>>

\subsection{Changing epsilon termination}

	\begin{figure}
		\centering
		\includegraphics[width=20cm]{picture/epsilon_event.png}
		\caption{SSP versus epsilon termination, $t=1$,$\lambda=1/t$}
		\label{fig:epsilon_event}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=20cm]{picture/epsilon_explicit.png}
		\caption{SSP versus epsilon termination, PTF parameter k=50,	$t=1$,$\lambda=1/t$}
		\label{fig:epsilon_explicit}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=20cm]{picture/epsilon_hybrid.png}
		\caption{SSP versus epsilon termination, PTF parameter k=50,	$t=1$,$\lambda=1/t$}
		\label{fig:epsilon_hybrid}
	\end{figure}

		\begin{figure}
			\centering
			\includegraphics[width=17cm]{picture/distance_hybrid2.png}
			\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,	$t=0.02$,$median lambda$,$\epsilon=10^{-6}$}
			\label{fig:dist_hybrid_50k}
		\end{figure}
